---
title: "R Notebook"
output: html_notebook
---

PRELIM DATA CHECK
```{r}
# Load libraries
library(tidyverse)
library(ggplot2)
library(lubridate)
library(skimr)
library(psych)
library(Hmisc)
library(corrplot)
library(naniar)
library(GGally)
library(janitor)

# Read in data set
df <- read_csv("company_data.csv")

# Check data set
head(df)

# Check missing values
df %>% gg_miss_var()

# Summary of basic descriptives of numeric data
df %>% psych::describe()

```

1. DATA CLEANING

SELECT CROSS-SECTIONAL SAMPLE (2021)
```{r}
# Filter observations for year 2022 and save into new data frame df_2022
df %>% filter(fyear == 2021) -> df_2021

# Prelim check for new data frame
df_2021 %>% gg_miss_var()
df_2021 %>% psych::describe()
```

HANDLE NA VALUES
```{r}
# Check columns that have NA values
names(which(colSums(is.na(df_2021)) > 0))

# Create new variables to indicate whether company reports each type of expenses
df_2021 %>%
  mutate(report_ad_expense = if_else(!is.na(xad), 1, 0),
         report_rd_expense = if_else(!is.na(xrd), 1, 0))-> df_2021

# Create new variables to indicate whether company reports any of the remaining info
df_2021 %>%
  mutate(report_income = if_else(!is.na(ni), 1, 0),
         report_sales = if_else(!is.na(sale), 1, 0))-> df_2021

# Create new variables to indicate whether company reports any of the additional chosen variables
df_2021 %>%
  mutate(report_goodwill = if_else(!is.na(gdwl), 1, 0),
         report_mkt_value = if_else(!is.na(mkvalt), 1, 0))-> df_2021

# Delete observation where TIC code is missing
df_2021 %>%
  filter(!is.na(tic)) -> df_2021
```

SELECT BY COMPANY EMPLOYEE SIZE
```{r}
# Filter and keep only companies with over 2,000 employees
df_2021 %>%
  filter(emp >= 2.00) -> df_2021

```

RENAME & DELETE VARIABLES
```{r}
# Rename necessary variables
df_2021 %>%
  rename(
    year = fyear,
    company = conm,
    price_adj_factor = ajex,
    assets = at,
    equity = ceq,
    common_shares = csho,
    employees = emp,
    goodwill = gdwl,
    net_income = ni,
    net_sales = sale,
    ad_expenses = xad,
    op_expenses = xopr,
    rd_expenses = xrd,
    other_expenses = xsga,
    market_value = mkvalt,
    closing_price = prcc_f
  ) -> df_2021

# Delete unnecessary variables
df_2021 %>%
  select(-indfmt, -consol, -popsrc, -datafmt, -curcd, -costat, -gvkey, -datadate) -> df_2021

```

RECODE VARIABLES
```{r}
# Create new variable representing the company industry (using SIC ranges)
df_2021 %>%
  mutate(
    sic = as.numeric(sic),
    industry = case_when(
      sic >= 0 & sic <= 999 ~ "Agriculture, Forestry and Fishing",
      sic >= 1000 & sic <= 1499 ~ "Mining",
      sic >= 1500 & sic <= 1799 ~ "Construction",
      sic >= 2000 & sic <= 3999 ~ "Manufacturing",
      sic >= 4000 & sic <= 4999 ~ "Transportation, Communications, Electric",
      sic >= 5000 & sic <= 5199 ~ "Wholesale",
      sic >= 5200 & sic <= 5999 ~ "Retail",
      sic >= 6000 & sic <= 6799 ~ "Finance, Insurance, Real Estate",
      sic >= 7000 & sic <= 7999 ~ "Services",
      sic >= 9100 & sic <= 9999 ~ "Public Administration")) -> df_2021

```


CREATE NEW ADVERTISING MEASURES
```{r}
# Create new variable representing strategic emphasis
df_2021 %>%
  mutate(strategic_emphasis = ((ad_expenses - rd_expenses) / assets)) -> df_2021

## Create a new binary variable indicating whether strategic_emphasis is greater than 0
df_2021 %>%
  mutate(strategic_emphasis_binary = if_else(strategic_emphasis >= 0, 1, 0)) -> df_2021

# Create new variable representing Tobin's Q
df_2021 %>%
  mutate(tobins_q = ((assets + (common_shares * closing_price) - equity) / assets)) -> df_2021

# Create new variable representing ROA
df_2021 %>%
  mutate(roa = net_income / assets) -> df_2021

# Create new variable representing R&D intensity
df_2021 %>%
  mutate(rd_intentisy = rd_expenses / net_sales) -> df_2021

# Create new variable representing advertising intensity
df_2021 %>%
  mutate(ad_intensity = ad_expenses / net_sales) -> df_2021

```

SEE AD, R&D EXPENSES OUT OF TOTAL EXPENSES
```{r}
# Create new variables for advertising and R&D expenses out of total expenses
df_2021 %>%
  mutate(
    total_exp = ad_expenses + rd_expenses + op_expenses + other_expenses,
    ad_exp_pct = (ad_expenses / total_exp) * 100,
    rd_exp_pct = (rd_expenses / total_exp) * 100) -> df_2021

```

COMBINE AD/R&D EXPENDITURE AND STRATEGIC EMPHASIS (TO HANDLE NULL VALUES)
```{r}
# Create new variable indicating whether the company has reported ad/R&D expenses
# and reported strategic emphasis
df_2021 %>%
  mutate(
    report_expense_emphasis = 
      if_else(report_ad_expense == 1 & report_rd_expense == 1 & !is.na(strategic_emphasis), 1, 0)
  ) -> df_2021

```


2. EDA

A. UNIVARIATE ANALYSIS



NEW ADVERTISING MEASURES
```{r}
# Strategic emphasis
df_2021 %>% 
  tabyl(strategic_emphasis_binary) %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_totals()


# Tobin's Q
## Check for null values, summary stats
sum(is.na(df_2021$tobins_q))
df_2021$tobins_q %>% psych::describe()

## Check for number of Tobin's Q values under 1
df_2021 %>%
  filter(tobins_q < 1) %>%
  summarise(
    under_one = n())

## Boxplot with outliers
df_2021 %>% 
  ggplot() + geom_boxplot(aes(tobins_q), outlier.colour = "red", outlier.shape = 1) +
  theme_classic() +
  theme(axis.text.y = element_blank()) +
  labs(
    title = "Tobin's Q Distribution Across Companies",
    x = "Tobin's Q")


# ROA
## Check for null values, summary stats
sum(is.na(df_2021$roa))
df_2021$roa %>% psych::describe()


# Advertising, R&D intensity
## Check for null values, summary stats
sum(is.na(df_2021$ad_intensity))
df_2021$ad_intensity %>% psych::describe()

sum(is.na(df_2021$rd_intentisy))
df_2021$rd_intentisy %>% psych::describe()

## Grouped histograms
df_2021 %>%
  select(
    ad_intensity,
    rd_intentisy) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  ggplot() + geom_histogram(aes(value)) + facet_wrap(variable~., scales = "free") +
  theme_classic() +
  labs(
    title = "Ad Intensity vs. R&D Intensity Across Companies",
    x = "Intensity",
    y = "Count")


```

OTHER COMPANY MEASURES
```{r}
# Advertising, R&D expenses
## Check for null values, summary stats
sum(is.na(df_2021$ad_expenses))
df_2021$ad_expenses %>% psych::describe()

sum(is.na(df_2021$rd_expenses))
df_2021$rd_expenses %>% psych::describe()

## Grouped histograms
df_2021 %>%
  select(
    ad_expenses,
    rd_expenses) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  ggplot() + geom_histogram(aes(value)) + facet_wrap(variable~., scales = "free") +
  theme_classic() +
  labs(
    title = "Ad vs. R&D Expenditure Across Companies",
    x = "Expenditure (Millions)",
    y = "Number of Companies")


# Employees
## Check for null values, summary stats
sum(is.na(df_2021$employees))
df_2021$employees %>% psych::describe()

## Histogram
df_2021 %>% 
  ggplot() + geom_histogram(aes(employees)) +
  theme_classic() +
  theme(axis.text.y = element_blank()) +
  labs(
    title = "Number of Employees Across Companies",
    x = "Employees")


# Goodwill
## Check for null values, summary stats
sum(is.na(df_2021$goodwill))
df_2021$goodwill %>% psych::describe()

## Boxplot
df_2021 %>% 
  ggplot() + geom_boxplot(aes(goodwill), outlier.colour = "red", outlier.shape = 1) +
  theme_classic() +
  theme(axis.text.y = element_blank()) +
  labs(
    title = "Goodwill Distribution Across Companies",
    x = "Goodwill (Millions)")
```

INDUSTRIES (BY SIC CODE)
```{r}
# Check for null values
sum(is.na(df_2021$industry))

# See frequencies
df_2021 %>% 
  tabyl(industry) %>%
  adorn_pct_formatting(digits = 2) %>% # Percent formatting
  adorn_totals()

# Bar charts by industry type
df_2021 %>%
  tabyl(industry) %>%
  drop_na() %>%
  arrange(n) %>%
  ggplot() + geom_col(aes(y = n, x = reorder(industry, n))) + coord_flip() +
  labs(
    title = "Company Distribution by Industry",
    x = "Industry",
    y = "Number of Companies")
```

BASIC DESCRIPTIVES TABLE (BY INDUSTRY)
```{r}
# Values: mean, median, std dev
# Variables: 
## strategic_emphasis (mean, std dev)
## ad_intensity
## rd_intensity
## tobin's q
## roa
## goodwill
## net_sales

df_2021 %>%
  group_by(industry) %>%
  drop_na() %>%
  summarise(mean_emphasis = mean(strategic_emphasis),
            mean_ad_int = mean(ad_intensity),
            mean_rd_int = mean(rd_intentisy),
            med_tobin = median(tobins_q),
            dev_tobin = sd(tobins_q),
            mean_roa = mean(roa),
            med_goodwill = median(goodwill),
            dev_goodwill = sd(goodwill)) -> sum_table

# Reformat table
colnames(sum_table) <- c("Industry", 
                         "Emphasis (Mean)",
                         "Ad Intensity (Mean)",
                         "R&D Intensity (Mean)",
                         "Tobin's Q (Median)",
                         "Tobin's Q (Std. Dev.)",
                         "ROA (Mean)",
                         "Goodwill (Median)",
                         "Goodwill (Std. Dev.)")
formattable(sum_table)


```



B. BIVARIATE ANALYSIS
- Scatterplots
- Correlational graphs
- Histograms
- Tables
- Etc.


PRELIM CORRELATIONAL MATRIX CHECK
```{r}
# Plot correlational matrix for relevant variables
df_2021 %>%
  select(
    assets,
    equity,
    goodwill,
    net_income,
    net_sales,
    ad_expenses,
    rd_expenses,
    market_value,
    tobins_q,
    roa,
    ad_intensity,
    # rd_intentisy
  ) %>%
  as.matrix %>% 
  rcorr() -> data.corr

corrplot(data.corr$r, method = "shade", order = "alphabet", type = "lower", addCoef.col = TRUE, tl.srt = 45, tl.pos = "ld")
```


ADVERTISING INTENSITY - AS DV
```{r}
# Advertising intensity as DV (group by industry)
## IV - Market value 
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = market_value, y = ad_intensity, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Market Value (Millions USD)",
    y = "Advertising Intensity")


## IV - Assets
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = assets, y = ad_intensity, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Assets (Millions USD)",
    y = "Advertising Intensity")


## IV - Equity
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = equity, y = ad_intensity, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Equity (Millions USD)",
    y = "Advertising Intensity")


## IV - Income
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = net_income, y = ad_intensity, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Net Income (Millions USD)",
    y = "Advertising Intensity")


## IV - Goodwill
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = goodwill, y = ad_intensity, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Goodwill (Millions USD)",
    y = "Advertising Intensity")


## IV - Common shares
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = common_shares, y = ad_intensity, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Shares (Millions USD)",
    y = "Advertising Intensity")
```

ADVERTISING INTENSITY - AS IV
```{r}
# Advertising intensity as IV (group by industry)
## DV - Income
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_intensity, y = net_sales, color = industry)) + 
  stat_smooth(aes(x = ad_expenses, y = tobins_q), method = "lm", se = FALSE, linewidth = 0.5) +
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Advertising Intensity",
    y = "Sales (Millions USD)")


## DV - Goodwill
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_intensity, y = goodwill, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Advertising Intensity",
    y = "Goodwill (Millions USD)")


## DV - Market value
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_intensity, y = market_value, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Advertising Intensity",
    y = "Market Value (Millions USD)")

```

ROA
```{r}
# ROA as DV (group by industry)
## IV - Advertising expenses
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_expenses, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_expenses, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) +
  labs(
    x = "R&D Expenditure (Millions USD)",
    y = "Sales (Millions USD)")


## IV - R&D expenses
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_expenses, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_expenses, y = roa), method = "lm", se = FALSE, linewidth = 0.5) +
  labs(
    x = "R&D Expenditure (Millions USD)",
    y = "Return on Assets")


## IV - Assets
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = assets, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Assets (Millions USD)",
    y = "Return on Assets")


## IV - Equity
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = equity, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Equity (Millions USD)",
    y = "Return on Assets")


## IV - Income
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = net_income, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Net Income (Millions USD)",
    y = "Return on Assets")


## IV - Goodwill
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = goodwill, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Goodwill (Millions USD)",
    y = "Return on Assets")


## IV - Market value
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = market_value, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  labs(
    x = "Market Value (Millions USD)",
    y = "Return on Assets")

```

TOBIN'S Q
```{r}
# Tobin's Q as DV (group by industry)
## IV - Advertising expenses
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_expenses, y = tobins_q, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = ad_expenses, y = tobins_q), method = "lm", se = FALSE, linewidth = 0.5) +
  labs(
    x = "Advertising Expenses (Millions USD)",
    y = "Tobin's Q")


## IV - R&D expenses
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_expenses, y = tobins_q, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_expenses, y = tobins_q), method = "lm", se = FALSE, linewidth = 0.5) +
  labs(
    x = "R&D Expenses (Millions USD)",
    y = "Tobin's Q")


## IV - Income
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = net_income, y = tobins_q, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = net_income, y = tobins_q), method = "lm", se = FALSE, linewidth = 0.5) +
  labs(
    x = "Net Income (Millions USD)",
    y = "Tobin's Q")
  

## IV - Goodwill
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = goodwill, y = tobins_q, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = goodwill, y = tobins_q), method = "lm", se = FALSE, linewidth = 0.5) +
  labs(
    x = "Goodwill (Millions USD)",
    y = "Tobin's Q")
  
  
## IV - Employees
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = employees, y = tobins_q, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = employees, y = tobins_q), method = "lm", se = FALSE, linewidth = 0.5) +
  labs(
    x = "Number of Employees",
    y = "Tobin's Q")
  

```

SALES
```{r}
# Sales as DV (group by industry)
## IV - Advertising expenses
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_expenses, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = ad_expenses, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Advertising Expenses (Millions USD)",
    y = "Sales (Millions USD)")


## IV - R&D expenses
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_expenses, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_expenses, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "R&D Expenses (Millions USD)",
    y = "Sales (Millions USD)")


## IV - Advertising intensity
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_intensity, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = ad_intensity, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Advertising Intensity",
    y = "Sales (Millions USD)")


## IV - Assets
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = assets, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = assets, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Assets (Millions USD)",
    y = "Sales (Millions USD)")


## IV - Income
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = net_income, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = net_income, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Net Income (Millions USD)",
    y = "Sales (Millions USD)")


## IV - Goodwill
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = goodwill, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = goodwill, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Goodwill (Millions USD)",
    y = "Sales (Millions USD)")


## IV - Market value
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = market_value, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = market_value, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Market Value (Millions USD)",
    y = "Sales (Millions USD)")

```

STRATEGIC EMPHASIS - CREATE TABLE
```{r}
# Install and load in formattable
install.packages("formattable")
library(formattable)

# Make table representing strategic emphasis category count for each industry
df_2021 %>%
  drop_na() %>%
  tabyl(industry, strategic_emphasis_binary) %>%
  adorn_totals("col") %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns(position = "front") -> table_test

# Save table as data frame and reformat
table_2 <- as.data.frame.matrix(table_test)
colnames(table_2) <- c("Industry", "R&D Emphasis", "Marketing Emphasis", "Total")
formattable(table_2)
```

CORRELATIONAL PLOTS CATEGORIZED BY STRATEGIC EMPHASIS
```{r}
# Employee against sales, grouped by industry and
# coded by strategic emphasis
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = employees, y = net_sales, color = strategic_emphasis_binary)) +
  facet_wrap(industry~., scales = "free") +
  labs(
    x = "Employee Number",
    y = "Sales (Millions USD)")


# Assets against sales, grouped by industry and
# coded by strategic emphasis
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = assets, y = net_sales, color = strategic_emphasis_binary)) +
  facet_wrap(industry~., scales = "free") +
  labs(
    x = "Assets",
    y = "Sales (Millions USD)")


# Goodwill against sales, grouped by industry and
# coded by strategic emphasis
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = goodwill, y = net_sales, color = strategic_emphasis_binary)) +
  facet_wrap(industry~., scales = "free") +
  labs(
    x = "Goodwill (Millions USD)",
    y = "Sales (Millions USD)")


# Sales against market value, grouped by industry and
# coded by strategic emphasis
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = net_sales, y = market_value, color = strategic_emphasis_binary)) +
  facet_wrap(industry~., scales = "free") +
  labs(
    x = "Sales (Millions USD)",
    y = "Market Value (Millions USD)")


# Advertising expenses against ROA, grouped by industry and
# coded by strategic emphasis
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_expenses, y = roa, color = strategic_emphasis_binary)) +
  facet_wrap(industry~., scales = "free") +
  labs(
    x = "Advertising Expenses (Millions USD)",
    y = "Return on Assets")


```


AD EXPENDITURE PERCENTAGES
```{r}
# Ad expenditure percentage as IV (group by industry)
## DV - Market value
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_exp_pct, y = market_value, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = ad_exp_pct, y = market_value), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Advertising Expenditure (Out of Total Expenditure)",
    y = "Market Value (Millions USD)")


## DV - Sales
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_exp_pct, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = ad_exp_pct, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Advertising Expenditure (Out of Total Expenditure)",
    y = "Sales (Millions USD)")


## DV - Income
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_exp_pct, y = net_income, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = ad_exp_pct, y = net_income), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Advertising Expenditure (Out of Total Expenditure)",
    y = "Income (Millions USD)")


## DV - ROA
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = ad_exp_pct, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = ad_exp_pct, y = roa), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "Advertising Expenditure (Out of Total Expenditure)",
    y = "Return on Assets")

```

R&D EXPENDITURE PERCENTAGES
```{r}
# R&D expenditure percentage as IV (group by industry)
## DV - Market value
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_exp_pct, y = market_value, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_exp_pct, y = market_value), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "R&D Expenditure (Out of Total Expenditure)",
    y = "Market Value (Millions USD)")


## DV - Sales
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_exp_pct, y = net_sales, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_exp_pct, y = net_sales), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "R&D Expenditure (Out of Total Expenditure)",
    y = "Sales (Millions USD)")


## DV - Income
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_exp_pct, y = net_income, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_exp_pct, y = net_income), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "R&D Expenditure (Out of Total Expenditure)",
    y = "Net Income (Millions USD)")


## DV - ROA
df_2021 %>%
  drop_na() %>%
  ggplot() + geom_point(aes(x = rd_exp_pct, y = roa, color = industry)) + 
  facet_wrap(industry~., ncol = 2, scales = "free_x") +
  stat_smooth(aes(x = rd_exp_pct, y = roa), method = "lm", se = FALSE, linewidth = 0.5) + 
  labs(
    x = "R&D Expenditure (Out of Total Expenditure)",
    y = "ROA")

```



